\textbf{SPECFEM3D}\\ \textbf{User Manual}

### 2010-11-06 doc/USER_MANUAL/manual_SPECFEM3D.tex
committed a new version of param_reader.c by Dennis McRitchie that works on Mac OS. Also updated the citation section of the manual.

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,KoWoHu02,ChCaVi03,Kop06}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,BeLaPi06,DuKa06,DeSeWh08,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions.
Note that in many (most?) geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies)
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient.
Effects due to lateral variations in compressional-wave speed, shear-wave
speed, density, a 3D crustal model, topography and bathymetry are
included. For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08} and
in particular \citet{KoLiTrSuStSh04}. The package can accommodate
full 21-parameter anisotropy (see~\citet{ChTr07}) as well as lateral
variations in attenuation. Adjoint capabilities and finite-frequency
kernel simulations are included \citep{LiTr06,TrKoLi08}.

@@

SPECFEM3D won the Gordon Bell award for best performance at the SuperComputing~2003
conference in Phoenix, Arizona (USA) by running at 5 teraflops (sustained)
on 1944 processors of the Japanese Earth Simulator using 14.6 billion
degrees of freedom stored in 2.5 terabytes of memory; see \cite{KoTsChTr03}
and the Gordon Bell Awards News Release \url{www.sc-conference.org/sc2003/nr_finalaward.html }
for details. It was a finalist again in 2008 for a run at 0.16 petaflops (sustained) on 149,784 processors of the `Jaguar' Cray XT5 system at Oak Ridge National Laboratories (USA) \citep{CaKoLaTiMiLeSnTr08}.
It also won the BULL Joseph Fourier supercomputing award in 2010.

The next release of the code will include support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10}
as well as Convolutional or Auxiliary Differential Equation Perfectly Matched absorbing Layers (C-PML or ADE-PML) \citep{KoMa07,MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10}.
The next release will use the PT-Scotch and ParMetis parallel libraries for mesh partitioning.

>>>>

The software package SPECFEM3D simulates seismic
wave propagation at the local or regional scale
based upon the spectral-element method (SEM).
The SEM is a continuous Galerkin technique, which can easily be made discontinous \citep{BeMaPa94,KoWoHu02,ChCaVi03,Kop06}; it is then a particular case of the discontinuous Galerkin technique \citep{ReHi73,FaRi99,HuHuRa99,CoKaSh00,GiHeWa02,RiWh03,MoRi05,GrScSc06,BeLaPi06,DuKa06,DeSeWh08,WiStBuGh10,DeSe10,EtChViGl10}, with optimized efficiency because of its tensorized basis functions.
Note that in many (most?) geological models in the context of seismic wave propagation studies
(except for fault dynamic rupture studies)
a discontinous mesh is not needed because material property contrasts are not drastic and thus a continuous formulation is sufficient. For a detailed introduction to the SEM as applied to regional
seismic wave propagation, please consult \citet{KoVi98,KoTr99,ChKoViCaVaFe07,TrKoLi08} and
in particular \citet{KoLiTrSuStSh04}.

Effects due to lateral variations in compressional-wave speed, shear-wave
speed, density, a 3D crustal model, topography and bathymetry are
included. The package can accommodate
full 21-parameter anisotropy (see~\citet{ChTr07}) as well as lateral
variations in attenuation. Adjoint capabilities and finite-frequency
kernel simulations are included \citep{LiTr06,TrKoLi08}.

@@

SPECFEM3D won the Gordon Bell award for best performance at the SuperComputing~2003
conference in Phoenix, Arizona (USA) (see \cite{KoTsChTr03}
and \url{www.sc-conference.org/sc2003/nr_finalaward.html}).
It was a finalist again in 2008 for a run at 0.16 petaflops (sustained) on 149,784 processors of the `Jaguar' Cray XT5 system at Oak Ridge National Laboratories (USA) \citep{CaKoLaTiMiLeSnTr08}.
It also won the BULL Joseph Fourier supercomputing award in 2010.

The next release of the code will include support for GPU graphics card acceleration \citep{KoMiEr09,KoErGoMi10,MiKo10}
as well as Convolutional or Auxiliary Differential Equation Perfectly Matched absorbing Layers (C-PML or ADE-PML) \citep{KoMa07,MaKoEz08,MaKoGe08,MaKo09,MaKoGeBr10}.
The next release will use the PT-Scotch parallel library for mesh partitioning.
